Stellar Bars in Isolated Gas-Rich Spiral Galaxies Do Not Slow Down

### 2023-04-19 paper/ms.tex
Add trapped fraction argument

We applied a Savitzky-Golay filter \citep{1964AnaCh..36.1627S} as implemented in
\texttt{scipy} using a window length of $21$ and polynomial order of $3$ to the
plot of torques in order to remove some numerical noise.

@@

We test this interpretation by measuring the angle offset between the halo
wake and the bar. If the wake and the bar are aligned (i.e., there is no angle
offset), then the wake cannot exert a negative torque on the bar. This angle
is plotted in the left panel of Fig.~\ref{fig:wake}, which shows that the
angle offset is larger in the \Nbody{} case than in the \SMUGGLE{} case by about a
factor of two. The center and right panels of Fig.~\ref{fig:wake} show the halo
wake with respect to the location of the bar in the \Nbody{} (center) and \SMUGGLE{}
(right) cases at one point in time.

>>>>

We applied a Savitzky-Golay filter \citep{1964AnaCh..36.1627S} as implemented in
\texttt{scipy} using a window length of $21$ and polynomial order of $3$ to the
plot of torques (Fig.~\ref{fig:prop}) and angle differences
(Fig.~\ref{fig:wake}) in order to remove some numerical noise.

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{fig/halo_trapped.pdf}
    \caption{The trapped fraction of the dark matter halo within two disk scale
    lengths ($\sim5.3\,\textrm{kpc}$) for the \Nbody{} and \SMUGGLE{} runs. As
    the dark matter halo torques the bar, material from the halo is trapped on
    bar-like orbits. In the \Nbody{} case, the trapped fraction increases with
    time, indicating the torquing process is active. In the \SMUGGLE{} case, the
    trapped fraction is nearly constant with time, indicating the torquing
    process is inactive.}
    \label{fig:htrap}
\end{figure}

@@

{\bf We test this interpretation in two ways. First, we measure the trapped
fraction of the halo. As material in the halo wake torques the bar, that
material becomes trapped on bar-like orbits \citep[the ``shadow
bar'';][]{2016MNRAS.463.1952P}. In Fig.~\ref{fig:htrap} we show the halo trapped
fraction for particles with radii less than two disk scale lengths
($\sim5.3\,\textrm{kpc}$). In the \Nbody{} case, the trapped fraction increases
with time, as expected since the halo is actively torquing the bar. In the
\SMUGGLE{} case, the trapped fraction is constant (or perhaps slightly
decreasing) with time. This supports our interpertation that the halo wake
process has shut down in the presence of the gas phase.}

Second, we measure the angle offset between the halo wake and the bar. If the
wake and the bar are aligned (i.e., there is no angle offset), then the wake
cannot exert a negative torque on the bar. This angle is plotted in the left
panel of Fig.~\ref{fig:wake}, which shows that the angle offset is larger in the
\Nbody{} case than in the \SMUGGLE{} case by about a factor of two. The center
and right panels of Fig.~\ref{fig:wake} show the halo wake with respect to the
location of the bar in the \Nbody{} (center) and \SMUGGLE{} (right) cases at one
point in time.
